Crowdsourced geometric morphometrics enable rapid large-scale collection and

### 2016-08-05 manuscript/manuscript.Rmd
Code drop

**Keywords**: crowdsourcing, morphometrics, phenotyping, morphology, comparative methods, macroevolution, Actinopterygii

@@

Integrating phenotypic data, such as anatomy, behavior, physiology, and other traits, with phylogenies is powerful strategy for investigating the patterns of biological evolution. Recent advances in next-generation sequencing [@Shendure2008; @Meyer2008] and sequence capture technologies [@Faircloth2012b; @Lemmon2012] have made phylogenetic inference of large radiations of organisms possible [@McCormack2012; @McCormack2013; @Faircloth2013; @Faircloth2014]. However, similar breakthroughs for generating new phenotypic datasets have been comparatively uncommon, likely due to the high expense and effort required [reviewed in @Burleigh2013].

@@

Although it is now possible to build phylogenetic trees with thousands of tips, and phenotypic data sets have similarly been growing larger and larger, the traits that are typically studied at this scale tend to be simple: geographic occurrences [@Jetz2012], one or two continuous characters [@Harmon2010; @Rabosky2013], a single discrete character [@Goldberg2010; @Edwards2011; @Price2012], or some combination of these [@Zanne2014; @Pyron2014]. A richer understanding of the forces that shape macroevolution requires the collection of more detailed phenotypic trait data at a broad scale.

Here we present a method and toolkit to efficiently collect two-dimensional geometric morphometric phenotypic data at a high-throughput "phenomic" scale. 
We developed a novel web browser-based image landmarking application, and use Amazon Mechanical Turk (<https://www.mturk.com>) to distribute digitization tasks to remote workers (hereafter *turkers*) over the Internet, who are paid for their contributions.
We evaluate the accuracy and precision of turkers by assigning identical image sets and digitization protocols to users who are experienced with fish morphology (hereafter *experts*), and compare the inter- and intra-observer differences between turkers and experts.
To illustrate the efficiency of this approach, we construct a phylogenetic analysis pipeline to download photographs and phylogenies of seven actinopterygiian families from the web, collect Mechanical Turk shape results, analyze the rate of diversification and body shape evolution using BAMM [@Rabosky2014a], and compare the time required for this workflow to traditional approaches. We also discuss the role that crowdsourcing is best suited in large-scale morphological analyses, and suggest ways to integrate crowdsourced data as part of larger initiatives to digitize biodiversity.

@@

Amazon Mechanical Turk ("MTurk") is a web-based service where Requesters can request work, known as Human Intelligence Tasks ("HITs") to be performed by Workers. Workers work from home and submit the tasks over the Internet, where Requesters review it, and, if they are satisfied with the results, accept the work and pay the Worker. We use MTurk as a platform to distribute our geometric morphometric tasks and financially compensate the worker accordingly. Scientific collection of data over MTurk and similar services has generally been limited to the fields of psychology and computer science, and there have been few attempts to crowdsource biological trait data [@Burleigh2013].

@@

We developed an geometric morphometric digitization application that runs completely on the user's local web browser, using the HTML5 Canvas interface. This simplifies the infrastructure challenge of needing to serve many crowdsourced workers simultaneously, since workers will not need to download desktop software such as tpsDig (<http://life.bio.sunysb.edu/ee/rohlf/software.html>) before generating data. The web application is configured with a simple JavaScript Object Notation (JSON) file that describes the landmarks necessary to complete an image digitization task (Supplemental Figure S1). Point landmarks, semilandmark curves, and linear measurements are all supported. The software is available at <https://github.com/jonchang/eol-mturk-landmark>.

@@

Collecting landmark-based geometric morphometric data at a broad scale permits detailed analysis of different sources of error, such as among- and within-observer variation [@VonCramon-Taubadel2007]. To assess whether the quality of data gathered by workers recruited through Amazon Mechanical Turk was significantly different than traditionally-collected data, we asked turkers ($n = `r nrow(filter(fish_reliability, role == "turker") %>% distinct(sha1mac))`$) and experts ($n = `r nrow(filter(fish_reliability, role == "morphologist") %>% distinct(sha1mac))`$) to landmark a set of five fish images, five times each. All participants used the same protocol and same software to digitize the same set of fishes. The landmarks were carefully selected based on previously-published literature concerning fish shape [Supplemental Figure S2; @Fink1995; @Cavalcanti1999; @Ruber2001a; @Klingenberg2003; @Chakrabarty2005; @Frederich2008; @Claverie2014; @Thacker2014]. We also ensured that the chosen landmarks included morphological features that were relatively straightforward to digitize (e.g., the position of the eye) and features that were likely to be more challenging to digitize (e.g., the most anterior and most dorsal points of the preopercle), in order to test for turker and expert differences over a spectrum of difficulties. We report the inter-observer reliability for turkers and experts by computing the ratio of the among-individual and the sum of the among-individual and measurement error variance components in a repeated measures nested MANOVA [@Palmer1986; @Zelditch2012].

To assess the differences between turker and experts on a per-landmark basis, we first compared for each landmark the median position of all turkers to the median position of all experts. We assumed that the expert median was the true position of that landmark, and calculated the absolute Euclidian distance in pixels. Larger distances would indicate low turker accuracy, while smaller distances would indicate high turker accuracy. We then examined the variance in turker landmarks. For each landmark, we rotated the cloud of points to maximize variance in one dimension, and calculated the log-ratio of median absolute deviations (MAD) between turkers and experts. This rotation is a conservative approach for assessing the difference in variance between these two groups, because it maximizes any apparent differences in landmark position. A positive log-ratio indicated that experts had lower variance than turkers, while a negative log-ratio indicated that turkers had lower variance. For all subsequent analysis, we excluded landmarks where turkers performed especially poorly, where either the accuracy or precision components for a given landmark exceeded 1.5 times the interquartile range of that component.

To determine whether turkers and experts were statistically distinguishable, we performed a non-parametric MANOVA using the randomized residual permutation procedure (RRPP) with 1,000 iterations [@Collyer2014]. The RRPP method reduces the effect of the "curse of dimensionality" ($p >> n$, where the number of predictors greatly exceeds the number of observations), a common problem in geometric morphometrics, and has been shown to have increased statistical power compared to a method where the raw data are randomized instead [@Anderson2003]. 
We test for a difference between mean turker and expert shapes against a null model of no difference between turker and expert changes, taking into account species-specific differences. 
A difference between models was considered significant if the p-value was less than $\alpha = 0.05$.

@@

A common strategy in fish comparative studies is to examine evolutionary dynamics within a single family [@Ferry-Graham2001a; @Alfaro2005; @Alfaro2007; @Rocha2008; @Hernandez2009; @Dornburg2011; @Sorenson2013; @Santini2013; @Frederich2013; @Claverie2014; @Thacker2014], potentially due to the extensive amount of time necessary to collect data. 
To test whether our method can improve on the case where the data collection method is geometric morphometrics, we use the average time it took an expert to measure a single fish image and predict the time it would take for a single individual expert to measure all images at 5x replication, and compare it to the time it took turkers to collect these measurements at the same replication level. If the turkers in aggregate annotated images more quickly than a single expert would have, this suggests that the parallelization afforded by crowdsourcing is effective at reducing the total time required for data collection.

To demonstrate the utility of obtaining comparative data using this method, we use previously published phylogenies for seven fish families: Acanthuridae [@Sorenson2013], Balistoidae, Tetraodontidae [@Santini2013], Apogonidae, Chaetodontidae, Labridae [@Cowman2011; @Choat2012], and Pomacentridae [@Frederich2013]. We matched `r nrow(distinct(fish_families, tip))` species to left-lateral images from the Encyclopedia of Life (<http://eol.org/>) using their application programming interface [Supplemental Table S1; @Parr2014]. Crowdsourced workers placed landmarks describing body shape variation following a standard protocol (Supplementary Material). The Cartesian position of these landmarks were used in a generalized Procrustes analyses [@Gower1975; @Rohlf1990], which centers, scales, and rotates landmark configurations to minimize the least-squares distance between shapes. We then determined the major components of shape variation using a Procrustes-aligned principal components analysis (PCA) [@Mardia1979; @Bookstein1991] with the R package *geomorph* `r citep(citation("geomorph"))`, and retain the principal component axes whose eigenvalues exceeded the corresponding random broken-stick component [@Jackson1993; @Legendre1998] for all subsequent analyses.

We used Bayesian Analysis of Macroevolutionary Mixtures [BAMM; @Rabosky2014a] to estimate rates of body shape evolution for all seven families. BAMM estimates the location of rate shifts in character evolution using a transdimensional (reversible jump) Markov Chain Monte Carlo method that samples a variety of models of lineage diversification and trait evolution. We assessed convergence and mixing using Tracer [@rambaut2007tracer]. We also repeated each analysis and simulated under the prior (without data) to exclude rate heterogeneity that occurred solely due to stochastic processes. We use a Bayes Factor criterion of $BF > 5$ to enumerate the set of credible shifts [@Shi2015] and visualized them in R using BAMMtools `r citep(citation("BAMMtools"))`.

@@

```{r turker_v_expert, fig.cap="Per-family breakdown of accuracy vs. precision for each landmark. Accuracy is represented as the difference between the median turker location for that landmark and the median expert location, with the expert location assumed to be the true location. Precision is represented as the log-ratio of median absolute deviations between turkers and experts. More positive numbers indicate better expert precision, whereas more negative numbers indicate better turker precision. Points highlighted in red are those determined to be outliers (1.5 $\times$ IQR). See Supplemental Information for a labeled version of this figure.", anchor="figure", message=FALSE, warning=FALSE}
no_st <- fish_reliability %>% filter(role != "student") %>% mutate(role = factor(role))

@@

ggplot(all_stats, aes(median, mad, color=outlier)) + geom_point() + labs(x="Accuracy: median turker - median expert", y="Precision: log turker variance / expert variance ") + facet_wrap(~family) + scale_color_manual(values = c("black", "red")) + theme_bw() + theme(legend.position="none") + xlim(0, 230)
ggsave("turker_precision.pdf", width=14, height=14, scale = 1/3)

# ggplot(highlighted, aes(median, mad)) + geom_point(color = "white") + labs(x="Accuracy: median turker - median expert", y="Precision: log turker variance ? expert variance ") + theme_black() + theme(legend.position = "none") + xlim(0, 130)
# ggsave("turker_precision_black.pdf", width=14, height=14, scale = 1/3)
# 
# 
# highlighted <- all_stats %>% mutate(should_color = family == "Tetraodontidae" & str_detect(mark, "O"))
# 
# ggplot(highlighted, aes(median, mad, color=should_color, label=mark)) + geom_point() + geom_text(data = filter(highlighted, should_color) %>% mutate(median = median + 4, mad = mad + 0.2)) + scale_color_manual(values = c("gray80", "red")) + labs(x="Accuracy: median turker - median expert", y="Precision: log turker variance ? expert variance ") + theme_black() + theme(legend.position = "none") + xlim(0, 130)
# 
# ggsave("turker_precision_black_puffers.pdf", width=14, height=14, scale = 1/3)
# 
# highlighted <- all_stats %>% mutate(should_color = family == "Chaetodontidae" & str_detect(mark, "[AD]3"))
# 
# ggplot(highlighted, aes(median, mad, color=should_color, label=mark)) + geom_point() + geom_text(data = filter(highlighted, should_color) %>% mutate(median = median + 4, mad = mad - 0.2)) + scale_color_manual(values = c("gray80", "red")) + labs(x="Accuracy: median turker - median expert", y="Precision: log turker variance ? expert variance ") + theme_black() + theme(legend.position = "none") + xlim(0, 130)
# 
# ggsave("turker_precision_black_chaets.pdf", width=14, height=14, scale = 1/3)
# 
# highlighted <- all_stats %>% mutate(should_color = family == "Balistidae" & str_detect(mark, "D[12]"))
# 
# ggplot(highlighted, aes(median, mad, color=should_color, label=mark)) + geom_point() + geom_text(data = filter(highlighted, should_color) %>% mutate(median = median + 4, mad = mad - 0.2)) + scale_color_manual(values = c("gray80", "red")) + labs(x="Accuracy: median turker - median expert", y="Precision: log turker variance ? expert variance ") + theme_black() + theme(legend.position = "none") + xlim(0, 130)
# 
# ggsave("turker_precision_black_triggers.pdf", width=14, height=14, scale = 1/3)
# 
# 
# highlighted <- all_stats %>% mutate(should_color = median > 10)
# 
# ggplot(highlighted, aes(median, mad, color=should_color, label=mark)) + geom_point() + geom_text(data = filter(highlighted, should_color) %>% mutate(median = median + 4, mad = mad - 0.2)) + scale_color_manual(values = c("gray80", "red")) + labs(x="Accuracy: median turker - median expert", y="Precision: log turker variance ? expert variance ") + theme_black() + theme(legend.position = "none") + xlim(0, 130)

# + geom_dl(aes(label=outlier_label), size=1, list("top.bumptwice", dl.trans(y=y+0.1), cex=0.75)) + scale_color_manual(values=c("black", "red")) + ylim(-max(abs(all_stats$mad) + 0.25), max(abs(all_stats$mad) + 0.25)) + theme("legend.position" = "none")
```

For nearly all landmarks, turkers only differ from the expert consensus by a few tens of pixels (Figure `r figr("turker_v_expert")`, Supplemental Figure S3). The most accurate and precise points are those that are related to the position of the eye (landmarks E1 and E2). The least accurate are those in the opercular series (O1-O5), particularly the ones related to the preopercle (O1-O3) likely because in certain groups (e.g., Tetraodontidae) the preopercle is difficult to visualize from external morphology alone. Experts were generally more precise than turkers, however there were some landmarks where the turkers converged on very similar locations. Based on these results we exclude in subsequent analyses the landmarks relating to the distal margins of all fins (A3, A4, P3, P4, D3, D4), the preopercle bones (O1-O3), the dorsal fin for triggerfishes (D1, D2), and the opercular opening for pufferfishes (O4-O5), due to low turker accuracy.

The inter-observer reliability of turkers and experts as measured by the ratio of among-individual and sum of the among-individual and measurement error ANOVA components was `r percent(reliability$turker)` and `r percent(reliability$expert)`, respectively. Although there is no current standard for acceptable levels of measurement reliability [@VonCramon-Taubadel2007], these percentages are not low enough to suggest weaknesses in the measurement protocol.

@@

```{r turk_morph_procrustes_space, fig.cap="Morphospace projection for each observer's mean shape. Blue points indicate experts, while red points indicate turkers. The mean shape for all turkers and experts for a given family is the point outlined in black for each family, and connected with a black line to help emphasize the difference between turker and expert mean shapes. The convex hull for each family is drawn to show the amount of among-observer shape variation.", anchor="figure"}
# Load data from the anonymized results file, remove students, drop bad marks
df <- fish_reliability %>%
	filter(role != "student") %>% 
	filter(!mark %in% c("O1","O2","O3", "A3", "A4", "D3", "D4", "P3", "P4"))

@@

```{r timing_plot, fig.cap="Line plot showing time to receive results for any given image (x axis) and the total fraction of the data set received (y axis). Landmarks were first received eight minutes after creation of the Amazon MTurk task, and at least one replicate was received for every image at the 80 minute mark.", anchor="figure"}
# median time (in minutes) it takes an expert to measure these fishes
timings <- (no_st %>% group_by(role) %>% summarise(duration=median(duration))) %>% mutate(total_time=duration * nrow(no_st))

@@

ggplot(timing_data, aes(time, frac)) + geom_line() + labs(x="Time taken (in minutes) to receive data for one unique replicate", y="Fraction of image set complete") + theme_minimal() + xlim(0, NA)

total_turker_time <- max(fish_families$time_taken) %>% as.numeric %>% dminutes %>% round(1)
```

Turkers in aggregate required `r as.character(total_turker_time)` to complete all `r nrow(distinct(fish_families, tip))` images at 5x replication `r figr("timing_plot")`. We estimate that a single expert would need `r as.character(morpho_per_image * nrow(distinct(fish_families, tip)))` to complete all images at 1x replication, extrapolated from a median expert time per image of `r as.character(morpho_per_image)`. At 5x replication, our projected expert would instead need `r as.character(morpho_per_image * nrow(fish_families))`.

```{r sevenfamily_tangent_plot, message=F, warning=F, fig.show="hold", fig.cap="Morphospace for seven families of ray-finned fishes. Each point indicates a separate species; families are separated by colors. The convex hull for each family is drawn to show area of morphospace occupied by each family. Figures for other PC axes are present in the Supplemental Material.", anchor="figure"}
name_map <- data_frame(family = c("acanthurid", "apogonidae", "balistoidae", "chaetodontidae", "labridae", "pomacentridae", "tetraodontidae"),
                       pretty_family = c("Acanthuridae", "Apogonidae", "Balistoidae", "Chaetodontidae", "Labridae", "Pomacentridae", "Tetraodontidae")
)

@@

```{r}

par_get_rtt_matrix <- function(ephy, start.time=NULL, end.time=NULL, nslices=100, node=NULL, nodetype = 'include', mc.cores = getOption("mc.cores", 2L)) {

	if (!'bammdata' %in% class(ephy)) {
		stop("Object ephy must be of class 'bammdata'\n");
	}
  if (ephy$type == 'diversification') {
	  stop("'diversification' not supported")
	}

>>>>

**Keywords**: comparative methods, macroevolution, Actinopterygii, Mechanical Turk, large scale annotation

@@

Integrating phenotypic data, such as anatomy, behavior, physiology, and other traits, with phylogenies is powerful strategy for investigating the patterns of biological evolution. Recent advances in next-generation sequencing [@Shendure2008; @Meyer2008] and sequence capture technologies [@Faircloth2012b; @Lemmon2012] have made phylogenetic inference of large radiations of organisms possible [@McCormack2012; @McCormack2013; @Faircloth2013; @Faircloth2015]. However, similar breakthroughs for generating new phenotypic datasets have been comparatively uncommon, likely due to the high expense and effort required [reviewed in @Burleigh2013].

@@

Although it is now possible to build phylogenetic trees with thousands of tips, and phenotypic data sets have similarly been growing larger and larger, studies at this scale tend to be limited to a few broad types of traits, including geographic occurrences [@Jetz2012], one or two continuous characters [@Harmon2010; @Rabosky2013], a single discrete character [@Goldberg2010; @Edwards2011; @Price2012], or some combination of these [@Zanne2014; @Pyron2014]. Most morphological evolutionary studies are constrained by a fundamental tradeoff in effort. Although the collection of detailed phenotypic measurements is often required to fully analyze complex form-function or ecology-phenotype relationships [@Schluter2000; @Alfaro2004; @Alfaro2005; @Wainwright2005; @Collar2006; @Price2010; @Frederich2013], rich methods of data collection such as computed tomography (CT) scanning are time intensive and do not permit easy scaling to hundreds or thousands of species. Analysis of more complex traits at this scale has the potential to greatly enrich our understanding of macroevolutionary processes, by permitting more refined hypothesis testing.

Here we present a method and toolkit to efficiently collect two-dimensional geometric morphometric phenotypic data at a high-throughput "phenomic" scale. 
We developed a novel web browser-based image landmarking application, and use Amazon Mechanical Turk (<https://www.mturk.com>) to distribute digitization tasks to remote workers (hereafter *turkers*) over the Internet, who are paid for their contributions.
We evaluate the accuracy and precision of turkers by assigning identical image sets and digitization protocols to users who are experienced with fish morphology (hereafter *experts*), and compare the inter- and intra-observer differences between turkers and experts.
To illustrate the efficiency of this approach, we construct a phylogenetic analysis pipeline to download photographs and phylogenies of seven actinopterygiian families from the web, collect Mechanical Turk shape results, analyze the body shape evolution using BAMM [@Rabosky2014a], and compare the time required for this workflow to traditional approaches. Though we focus on collecting two-dimensional geometric morphometric data, we address the challenges that will be common to all studies that crowdsource phenotypic data. We also discuss the role that crowdsourcing is best suited in large-scale morphological analyses, and suggest ways to integrate crowdsourced data as part of larger initiatives to digitize biodiversity.

@@

Amazon Mechanical Turk ("MTurk") is a web-based service where Requesters can request work, known as Human Intelligence Tasks ("HITs") to be performed by Workers. Workers work from home and submit the tasks over the Internet, where Requesters review it, and, if they are satisfied with the results, accept the work and pay the Worker [for a detailed overview, see @Mason2012a]. We use MTurk as a platform to distribute our geometric morphometric tasks and financially compensate the worker accordingly. Scientific collection of data over MTurk and similar services has generally been limited to the fields of psychology and computer science, and there have been few attempts to crowdsource biological trait data [@Burleigh2013].

@@

We developed an geometric morphometric digitization application that runs completely on the user's local web browser, using the HTML5 Canvas interface. This simplifies the infrastructure challenge of needing to serve many crowdsourced workers simultaneously, since workers will not need to download desktop software such as tpsDig (<http://life.bio.sunysb.edu/ee/rohlf/software.html>) before generating data. The web application is configured with a JavaScript Object Notation (JSON) file that describes the landmarks necessary to complete an image digitization task (Supplemental Figure S1). Point landmarks, semilandmark curves, and linear measurements are all supported. The software is available at <https://github.com/jonchang/eol-mturk-landmark>.

@@

Collecting landmark-based geometric morphometric data at a broad scale permits detailed analysis of different sources of error, such as among- and within-observer variation [@VonCramon-Taubadel2007]. To assess whether the quality of data gathered by workers recruited through Amazon Mechanical Turk was significantly different than traditionally-collected data, we asked turkers ($n = `r nrow(filter(fish_reliability, role == "turker") %>% distinct(sha1mac))`$) and experts ($n = `r nrow(filter(fish_reliability, role == "morphologist") %>% distinct(sha1mac))`$) to landmark a set of five fish images, five times each. Turkers were compensated \$25 for the entire task. All participants used the same protocol (Supplemental Material) and same software to digitize the same set of fishes (Supplemental Table S1, S2). The landmarks were carefully selected based on previously-published literature concerning fish shape [Supplemental Figure S2; @Fink1995; @Cavalcanti1999; @Ruber2001a; @Klingenberg2003; @Chakrabarty2005; @Frederich2008; @Claverie2014; @Thacker2014]. We also ensured that the chosen landmarks included morphological features that were relatively straightforward to digitize (e.g., the position of the eye) and features that were likely to be more challenging to digitize (e.g., the most anterior and most dorsal points of the preopercle), in order to test for turker and expert differences over a spectrum of difficulties. We report the inter-observer reliability for turkers and experts by computing the ratio of the among-individual and the sum of the among-individual and measurement error variance components in a repeated measures nested MANOVA [@Palmer1986; @Zelditch2012]. To test whether workers were consistently measuring the same shape, we examined the per-worker consistency, as estimated by the morphological disparity [Procrustes variance; @Zelditch2012] of each worker's measured shapes. We then summarized the consistency within groups, and compared the median consistency of turkers and experts. To determine whether turkers improved with experience, we excluded the three images that turkers worked on, and calculated thse distance between their mean shape and the mean shape of experts. We then repeated this, but without excluding the first three images that turkers digitized. To determine whether turkers worked faster with experience, we compared the time it took turkers to complete their first image compared to their fifth image.

To assess the differences between turker and experts on a per-landmark basis, we first compared for each landmark the median position of all turkers to the median position of all experts. We assumed that the expert median was the true position of that landmark, and calculated the absolute Euclidian distance in pixels. Larger distances would indicate low turker accuracy, while smaller distances would indicate high turker accuracy. Because the specimens digitized in this study varied in size, we also report turker accuracy as both distance in millimeters and as a fraction of the specimen's total length (TL). We then examined the variance in turker landmarks. For each landmark, we rotated the cloud of points to maximize variance in one dimension, and calculated the log-ratio of median absolute deviations (MAD) between turkers and experts. This rotation is a conservative approach for assessing the difference in variance between these two groups, because it maximizes any apparent differences in landmark position. A positive log-ratio indicated that experts had lower variance than turkers, while a negative log-ratio indicated that turkers had lower variance. For all subsequent analysis, we excluded landmarks where turkers performed especially poorly, where either the accuracy or precision components for a given landmark exceeded 1.5 times the interquartile range of that component.

To determine whether turkers and experts were statistically distinguishable, we performed a non-parametric MANOVA using the randomized residual permutation procedure (RRPP) with 1,000 iterations [@Collyer2015]. The RRPP method reduces the effect of the "curse of dimensionality" ($p >> n$, where the number of predictors greatly exceeds the number of observations), a common problem in geometric morphometrics, and has been shown to have increased statistical power compared to a method where the raw data are randomized instead [@Anderson2003]. 
We test for a difference between mean turker and expert shapes against a null model of no difference between turker and expert changes, taking into account species-specific differences. 
A difference between models was considered significant if the p-value was less than $\alpha = 0.05$.

@@

A common strategy in fish comparative studies is to examine evolutionary dynamics within a single family [@Ferry-Graham2001a; @Alfaro2005; @Alfaro2007; @Rocha2008; @Hernandez2009; @Dornburg2011; @Sorenson2013; @Santini2013; @Frederich2013; @Claverie2014; @Thacker2014], potentially due to the extensive amount of time necessary to collect data.
To demonstrate the utility of obtaining comparative data using our method, we use previously published phylogenies for seven fish families: Acanthuridae [@Sorenson2013], Balistoidae, Tetraodontidae [@Santini2013], Apogonidae, Chaetodontidae, Labridae [@Cowman2011; @Choat2012], and Pomacentridae [@Frederich2013]. We match species in these phylogenies to left-lateral images from the Encyclopedia of Life (<http://eol.org/>) using their application programming interface [Supplemental Table S5; @Parr2014]. Crowdsourced workers placed landmarks describing body shape variation following a standard protocol (Supplemental Material) and were compensated \$0.15 per completed image.

To test whether our method could be faster than a single expert digitizing a dataset, we extrapolated the time it would take for a single expert to measure all images at 1x replication, based on the average time an expert took to digitize a single image. We compared this predicted measurement time to the total time required for turkers to complete all digitization tasks at 5x replication, from initial upload to final submission. If the turkers in aggregate annotated images more quickly than a single expert would have, this suggests that the parallelization afforded by crowdsourcing is effective at reducing the total time required for data collection.

The Cartesian position of turker-collected landmarks were used in a generalized Procrustes analyses [@Gower1975; @Rohlf1990], which centers, scales, and rotates landmark configurations to minimize the least-squares distance between shapes. We then determined the major components of shape variation using a Procrustes-aligned principal components analysis (PCA) [@Mardia1979; @Bookstein1991] with the R package *geomorph* `r citep(citation("geomorph"))`, and retain the principal component axes whose eigenvalues exceeded the corresponding random broken-stick component [@Jackson1993; @Legendre1998] for all subsequent analyses.

To illustrate the potential of how crowdsourcing could be integrated into an pipeline that could allow rapid collection and analysis of phenotypic data, we used Bayesian Analysis of Macroevolutionary Mixtures [BAMM; @Rabosky2014a] to estimate rates of body shape evolution for all seven families. BAMM estimates the location of rate shifts in character evolution using a transdimensional (reversible jump) Markov Chain Monte Carlo method that samples a variety of models of trait evolution. Any missing trait data is treated as a latent variable in the analysis. We assessed convergence and mixing using Tracer [@Rambaut2014]. We also repeated each analysis and simulated under the prior (without data) to exclude rate heterogeneity that occurred solely due to stochastic processes. We use a Bayes Factor criterion of $BF > 5$ to enumerate the set of credible shifts [@Shi2015] and visualized them using BAMMtools [@Rabosky2014c].

@@

```{r turker_v_expert, fig.cap="Per-family breakdown of accuracy vs. precision for each landmark. Accuracy is represented as the difference between the median turker location for that landmark and the median expert location, with the expert location assumed to be the true location. Precision is represented as the log-ratio of median absolute deviations between turkers and experts. More positive numbers indicate better expert precision, whereas more negative numbers indicate better turker precision. Points highlighted in red are those determined to be outliers (1.5 $\times$ IQR). A labeled version of this figure is available as Supplemental Figure S3. Photo credit J.E. Randall (used with permission under a CC-BY-NC 3.0 license).", anchor="figure", message=FALSE, warning=FALSE, fig.width = 5, fig.height = 5, fig.keep="last"}
no_st <- fish_reliability %>% filter(role != "student") %>% mutate(role = factor(role))

@@

## quantile(all_stats$median, seq(0,1,0.1))[9]

plot_png = function(path, x, y, size)
{
  require('png')
  logo <- readPNG(path, native=T) # read the file
  dims<-dim(logo)[1:2] #number of x-y pixels for the logo (aspect ratio)
  AR<-dims[1]/dims[2]
  oldpar <- par(usr=c(0, 1, 0, 1))
  rasterImage(logo, x-(size/2), y-(AR*size/2), x+(size/2), y+(AR*size/2), interpolate=TRUE)
  par(oldpar)
}

plot.new()
par(mfrow = c(3, 3))
par(cex = 0.6)
par(mar = c(0, 0, 0, 0), oma = c(4, 4, 0.5, 0.5))
ctr <- 1
xlim <- c(0, 240)
ylim <- c(-2.4, 5.5)
for (fam in unique(all_stats$family)) {
  wanted <- all_stats %>% filter(family == fam)
  plot(1, xlim = xlim, ylim = ylim, type = "n", axes = FALSE)
  plot_png(sprintf("fish_cutouts/%s.png", fam), 0.75, 0.7, 0.5)
  points(mad ~ median, data = wanted, pch = 16, col = ifelse(wanted$outlier, "red", "black"))
  mtext(fam, side = 3, line = -1.5, cex = 0.6)
  if (ctr %in% c(1, 4, 7)) {
    axis(2)
  }
  if (ctr %in% 7:9) {
    axis(1)
  }
  box(col = "grey60")
  ctr <<- ctr + 1
}
mtext("Accuracy: median turker - median expert", side = 1, outer = TRUE, cex = 0.7, line = 2.2)
mtext("Precision: log turker variance / expert variance", side = 2, outer = TRUE, cex = 0.7, line = 2.2)

```{r pixel_conv, warning=FALSE}
pixel_ratios <- read_csv("fish_reliability_images.csv") %>% transmute(Family, cm = TL / px * 10, frac = cm / TL)
conv <- list(tenpx = range(round(pixel_ratios$cm * 10, 2)), frac = percent(range(round(pixel_ratios$frac, 3))))
```

For nearly 90% of the points measured, turkers differed from the expert consensus by less than 30 pixels, with half of all landmarks having less than 3 pixels of difference (10 px = `r conv$tenpx[1]`--`r conv$tenpx[2]` mm, `r conv$frac[1]`--`r conv$frac[2]` TL, Figure `r figr("turker_v_expert")`, Supplemental Figure S3, Supplemental Table S1). The most accurate and precise points are those that are related to the position of the eye (landmarks E1 and E2). The least accurate are those in the opercular series (O1-O5), particularly the ones related to the preopercle (O1-O3) likely because in certain groups (e.g., Tetraodontidae) the preopercle is difficult to visualize from external morphology alone. Experts were generally more precise than turkers, however there were some landmarks where the turkers converged on very similar locations. Based on these results we exclude in subsequent analyses the landmarks relating to the distal margins of all fins (A3, A4, P3, P4, D3, D4), the preopercle bones (O1-O3), the dorsal fin for triggerfishes (D1, D2), and the opercular opening for pufferfishes (O4-O5), due to low turker accuracy.

```{r turker_time, message=F, warning=FALSE}
turker_time <- (only_good_points %>% group_by(role, family, sha1mac, sequence) %>% distinct %>% group_by(role, sequence) %>% summarise(time=median(duration)) %>% filter(role == "turker"))$time %>% round(2)
```

The inter-observer reliability of turkers and experts as measured by the ratio of among-individual and sum of the among-individual and measurement error ANOVA components was `r percent(reliability$turker)` and `r percent(reliability$expert)`, respectively. Although there is no current standard for acceptable levels of measurement reliability [@VonCramon-Taubadel2007], these percentages are not low enough to suggest weaknesses in the measurement protocol. Turkers were less consistent than the average expert (Supplemental Table S3); however, the overall difference in consistency between turkers and experts was generally quite small. We did not find evidence that turkers improved over time. Excluding the first three images did not markedly change turkers' performance compared to experts (Supplemental Table S4). Turkers took extra time to complete their first task, with a median completion time of `r turker_time[1]` minutes, compared to `r turker_time[5]` minutes on their fifth task.

@@

```{r turk_morph_procrustes_space, fig.cap="Morphospace projection for each observer's mean shape. Blue points indicate experts, while red points indicate turkers. The mean shape for all turkers and experts for a given family is the point outlined in black for each family, and connected with a black line to help emphasize the difference between turker and expert mean shapes. The convex hull for each family is drawn to show the amount of among-observer shape variation. The other PC axes are shown in Fig S4.", anchor="figure"}
# Load data from the anonymized results file, remove students, drop bad marks
df <- fish_reliability %>%
	filter(role != "student") %>% 
	filter(!mark %in% c("O1","O2","O3", "A3", "A4", "D3", "D4", "P3", "P4"))

@@

```{r tips_per_family}
tips_per_family <- distinct(fish_families, tip) %>% group_by(family) %>% summarise(images=n()) %>% mutate(pretty_name = names(fish_phy), tips = lapply(fish_phy, function(x) length(x$tip.label)) %>% unlist, text = sprintf("%s: %d/%d", pretty_name, images, tips))
```

We were able to match `r nrow(distinct(fish_families, tip))` out of `r lapply(fish_phy, function(x) length(x$tip.label)) %>% unlist %>% sum` species to images in EOL's database (`r paste(tips_per_family$text, collapse=", ")`). Due to the low number of images matched for acanthurids, apogonids, and chaetodontids, we focused on the other four families with better taxon sampling for the comparative BAMM analysis.

```{r timing_plot, fig.cap="Line plot showing time to receive results for any given image (x axis) and the total fraction of the data set received (y axis). Landmarks were first received eight minutes after creation of the Amazon MTurk task, and at least one replicate was received for every image at the 80 minute mark.", anchor="figure", fig.width = 5, fig.height = 4}
# median time (in minutes) it takes an expert to measure these fishes
timings <- (no_st %>% group_by(role) %>% summarise(duration=median(duration))) %>% mutate(total_time=duration * nrow(no_st))

@@

ggplot(timing_data, aes(time, frac)) + geom_line() + labs(x="Time taken (in min) to receive data for one unique replicate", y="Fraction of image set complete") + theme_minimal() + xlim(0, NA)

total_turker_time <- max(fish_families$time_taken) %>% as.numeric %>% dminutes %>% round(1)

worker_time_spent <- sum(distinct(fish_families, tip, time_taken)$worker_time_spent) %>% dminutes %>% round(1)
```

At 5x replication, `r as.character(total_turker_time)` elapsed between initial upload of the task to Amazon Mechanical Turk and submission of the last task by a turker (Figure `r figr("timing_plot")`). We estimate that a single expert would need `r as.character(morpho_per_image * nrow(distinct(fish_families, tip)))` to complete all images at 1x replication, extrapolated from a median expert time per image of `r as.character(morpho_per_image)`. Our projected expert would need `r round(morpho_per_image * nrow(distinct(fish_families, tip)) * 5, 1) %>% as.character` were they to instead work at 5x replication.

```{r sevenfamily_tangent_plot, message=F, warning=F, fig.show="hold", fig.cap="Morphospace for seven families of ray-finned fishes. Each point indicates a separate species; families are separated by colors. The convex hull for each family is drawn to show area of morphospace occupied by each family. The other PC axes are shown in Supplemental Figures S5, S6.", anchor="figure"}
name_map <- data_frame(family = c("acanthurid", "apogonidae", "balistoidae", "chaetodontidae", "labridae", "pomacentridae", "tetraodontidae"),
                       pretty_family = c("Acanthuridae", "Apogonidae", "Balistoidae", "Chaetodontidae", "Labridae", "Pomacentridae", "Tetraodontidae")
)

@@

```{r load_bamm_data, message=FALSE, echo=FALSE, warning=FALSE, results="hide"}
#base <- "data-raw/bamm/"
base <- "../data-raw/bamm/"
fams <- c("balistoidae", "labridae", "pomacentridae", "tetraodontidae")
pretty_names <- c("Balistoidae", "Labridae", "Pomacentridae", "Tetraodontidae")
names(fams) <- pretty_names

tre_trait <- fish_phy[pretty_names]
names(tre_trait) <- fams
